\bf $\mathsf{TEDAT}$: Boosting Bandwidth-based Availability Over Inter-DC WAN

### 2021-01-18 paper.tex
introuction revision by Han
introuction revision AND SEC-3by Han

Thirdly, 
we implement $\mathsf{TEDAT}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using real trace driven simulations as well as  on a small testbed  (see $\S$\ref{evaluation}).
We compare  $\mathsf{TEDAT}$ with state-of-the-art TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{TEDAT}$ can 
(1) speed up the online admission control by 30 $\times $ at the expense of 5\% higher rejection ratio;
(2) meet the availability SLAs for 40\% more bandwidth demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{TEDAT}$ is the first to tackle bandwidth based availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under TEDAT, links can maintain high utilization.

@@

 \begin{itemize}
\item \textbf{High acceptance ratio:}  
  Tenants' demands might arrive at anytime. 
  The system should be able to accommodate as many demands as possible under the constraint of availability and bandwidth targets.
\item \textbf{Maintain high availability:}
The system must make services with stringent availability requirements (e.g., 99.999\%) pass links with high reliability.
Therefore, their bandwidth demands can be guaranteed with high probability.
\item \textbf{Handle failures:}
When there are link failures, the system can reroute traffic that would go over failed links over the remaining active tunnels with small revenue loss instead.
\item \textbf{Practical \& scalability:}
The system must be able to admit or reject tenants' new demands in near real-time fashion and the system needs to scale up to dozens of DCs.

 \end{itemize}

\subsection{Availability abstraction}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a tenant could be a customer who launches multiple virtual private clouds over  multiple DCs in public clouds (e.g., Amazon AWS) or could be a service team who launches multiple VM instances in private clouds (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
Services have different bandwidth demands as well as availability targets.
However, there exists no interface for tenants to specify them.
We now present $\mathsf{TEDAT}$ 's availability abstraction, which aims to guarantee the bandwidth-based availability of services.

\textbf{Demand model:}
We model the inter-DC WAN as a  graph $G=(V,E)$,  where $V$ and $E$ are the nodes and link sets.
Each link $e\in E$ is associated with a link capacity $c_e$ (e.g., in bps).
DC pair set is $K$ and  $\beta_j$ presents the desired availability target  of service $j \in J$.
Each tenant's demand can be presented as a tuple $\{\alpha, \theta, \delta, \gamma, \mu\}$,
where $\alpha$ and $\delta$ are the arrival and departure of the demand, $\gamma$ denotes the service type and $\theta =\{d_{1}, d_{2}, ...,d_{K} \}$ presents bandwidth over each node pair.
%We assume one tenant can only start one service and if a tenant wants to boot multiple services, we can use multiple tuples to describe it.
Service providers will offer refunding for any violating availability targets (see $\S$\ref{background}) and we use $\mu$ to denote the penalty.
%The system should reserve enough bandwidth to guarantee all \textit{admitted} requests' availability demands.
%When all services'  \textit{achieved} bandwidth-based availability are larger than their corresponding desired availability target, the system is able to accommodate this service request, otherwise, the request will be denied.

@@

\subsection{System design}
The system contains one controller, multiple brokers and multiple clients.
Figure \ref{pic-overview} shows the architecture of $\mathsf{TEDAT}$ system.
It works as follows:
When a tenant submits a demand to the controller, the Admission Control module will check whether the request can be admitted or not (see $\S$ \ref{admission_control}).
If the demand is admitted, the system will pre-allocate resource to the tenant and pass it to Online Scheduler module, while the rejected demands can be resubmitted by the tenants latter.
The Online Scheduler module performs traffic engineering algorithm (see $\S$ \ref{TE}) every  $T$ (e.g., 10) minutes to enforce bandwidth of each demand.
To prevent much revenue loss, the Online Scheduler module also derives the backup allocation under the assumption that  some fragile links could fail (see $\S$ \ref{backup}) every $T$. 
Each data center has a broker that manages the hosts inside.
Brokers track topology and apportions the allocated rate to each host.
Each host belongs to a service and it maintains a client to enforce bandwidth.

\section{$\mathsf{TEDAT}$}\label{HATE}
In this section, we make a full description of $\mathsf{TEDAT}$ framework, which contains three parts, i.e., admission control, traffic engineering and failure recovery.
We consider tunnel-based forwarding \cite{FFC,swan,Teavar}, where traffic is carried over a set of tunnels.
%Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
For each node pair $k\in K$ of the inter-DC WAN $G=(V,E)$, we are given a set of pre-selected tunnels $T_{k}$, where tunnel set $T_{k}$ can be derived with different routing schemes (e.g., k-shortest paths, edge disjoint paths \cite{Bruno2013Dynamic}, oblivious routing \cite{SMORE}). 
%In Section \ref{evaluation}, we evaluate the impact of routing schemes  on performance.
Each tunnel $t\in T_{k}$ contains a set of links and  $L_{te}$ presents whether tunnel $t$ contains link $e\in E$ or not.
%The network scenario set is $\bm{Z}$ and the corresponding probability is $p(\bm{z}), \forall \bm{z}\in \bm{Z} $.
$f_{ikt}$ is the bandwidth allocated over tunnel $t \in T_{k}$ for demand $i$ and 
$I_a$ is the total \textit{admitted} demand set form tenants.
Let $x_t(\bm{z})$ denote whether tunnel $t$ is available (i.e., $x_t(\bm{z})=1$)  or not  (i.e., $x_t(\bm{z})=0$) under network scenario $\bm{z}$.
Table \ref{Notation} shows the main notations.
The framework intends to achieve three goals: 
(1) Accommodate as many demands as possible subject to network failure model, diverse service availability and bandwidth targets;
(2) Guarantee the bandwidth-based availability target  for each admitted demand;
(3) Minimize revenue loss when network fails.
%\begin{enumerate}
%    \item  How to accommodate as many requests as possible subject to network failure model and diverse service availability targets  (see $\S$ \ref{admission_control}).
%    \item  How to route all admitted requests with minimum induced network overload under the constraint of network failure model and diverse service availability targets (see $\S$ \ref{TE}).
%    \item  How to reroute requests with minimum cost when network fails (see $\S$ \ref{backup}).
%\end{enumerate}

@@

@@

@@

\begin{figure} 
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.8 in]{fig/evaluation/routing.pdf}
    \caption{Routings.} 
    \label{routing-version} 
  \end{minipage}% 
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.8 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}

>>>>

Thirdly, 
we implement $\mathsf{TEDAT}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as real trace driven simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{TEDAT}$ with state-of-the-art TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{TEDAT}$ can 
(1) speed up the online admission control by 30 $\times $ at the expense of 5\% higher rejection ratio;
(2) meet the availability SLAs for 40\% more bandwidth demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{TEDAT}$ is the first to tackle bandwidth based availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under TEDAT, links can maintain high utilization.

@@

\section{$\mathsf{TEDAT}$}\label{HATE}
In this section, we make a full description of $\mathsf{TEDAT}$ framework, which contains three parts, i.e., admission control, traffic scheduling and failure recovery.
Table \ref{Notation} shows the main notations.
The framework intends to achieve the following objectives: 
 \begin{itemize}
\item \textbf{High acceptance ratio:}  
  Tenants' demands might arrive at anytime. 
  The system should be able to accommodate as many demands as possible under the constraint of availability and bandwidth targets.
\item \textbf{Maintain high availability:}
The system must make services with stringent availability requirements (e.g., 99.999\%) pass links with high reliability.
Therefore, their bandwidth demands can be guaranteed with high probability.
\item \textbf{Handle failures:}
When there are link failures, the system can reroute traffic that would go over failed links over the remaining active tunnels with small revenue loss instead.
%\item \textbf{ \& scalability:}
%
\end{itemize}

\subsection{BA abstraction}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a tenant could be a customer who launches multiple virtual private clouds over  multiple DCs in public clouds (e.g., Amazon AWS) or could be a service team who launches multiple VM instances in private clouds (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
Services have different bandwidth demands as well as availability targets.
However, there exists no interface for tenants to specify them.
We now present $\mathsf{TEDAT}$ 's availability abstraction, which aims to guarantee the bandwidth-based availability of services.

\textbf{BA demand model:}
We model the inter-DC WAN as a  graph $G=(V,E)$,  where $V$ and $E$ are the nodes and link sets.
Each link $e\in E$ is associated with a link capacity $c_e$ (e.g., in bps).
DC pair set is $K$ and  $\beta_j$ presents the desired availability target  of service $j \in J$.
Each tenant's demand can be presented as a tuple $\{\alpha, \theta, \delta, \gamma, \mu\}$,
where $\alpha$ and $\delta$ are the arrival and departure of the demand, $\gamma$ denotes the service type and $\theta =\{d_{1}, d_{2}, ...,d_{K} \}$ presents bandwidth over each node pair.
%We assume one tenant can only start one service and if a tenant wants to boot multiple services, we can use multiple tuples to describe it.
Service providers will offer refunding for any violating availability targets (see $\S$\ref{background}) and we use $\mu$ to denote the penalty.
%The system should reserve enough bandwidth to guarantee all \textit{admitted} requests' availability demands.
%When all services'  \textit{achieved} bandwidth-based availability are larger than their corresponding desired availability target, the system is able to accommodate this service request, otherwise, the request will be denied.

@@

We consider tunnel-based forwarding \cite{FFC,swan,Teavar}, where traffic is carried over a set of tunnels.
%Consider an undirected graph $G = (V,E)$ and a set of $k$ pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
For each node pair $k\in K$ of the inter-DC WAN $G=(V,E)$, we are given a set of pre-selected tunnels $T_{k}$, where tunnel set $T_{k}$ can be derived with different routing schemes (e.g., k-shortest paths, edge disjoint paths \cite{Bruno2013Dynamic}, oblivious routing \cite{SMORE}). 
%In Section \ref{evaluation}, we evaluate the impact of routing schemes  on performance.
Each tunnel $t\in T_{k}$ contains a set of links and  $L_{te}$ presents whether tunnel $t$ contains link $e\in E$ or not.
%The network scenario set is $\bm{Z}$ and the corresponding probability is $p(\bm{z}), \forall \bm{z}\in \bm{Z} $.
$f_{ikt}$ is the bandwidth allocated over tunnel $t \in T_{k}$ for demand $i$ and 
$I_a$ is the total \textit{admitted} demand set form tenants.
Let $x_t(\bm{z})$ denote whether tunnel $t$ is available (i.e., $x_t(\bm{z})=1$)  or not  (i.e., $x_t(\bm{z})=0$) under network scenario $\bm{z}$.

%\begin{enumerate}
%    \item  How to accommodate as many requests as possible subject to network failure model and diverse service availability targets  (see $\S$ \ref{admission_control}).
%    \item  How to route all admitted requests with minimum induced network overload under the constraint of network failure model and diverse service availability targets (see $\S$ \ref{TE}).
%    \item  How to reroute requests with minimum cost when network fails (see $\S$ \ref{backup}).
%\end{enumerate}

@@

The system contains one controller, multiple brokers and multiple clients.
Figure \ref{pic-overview} shows the architecture of $\mathsf{TEDAT}$ system.
It works as follows:
When a tenant submits a demand to the controller, the Admission Control module will check whether the request can be admitted or not (see $\S$ \ref{admission_control}).
If the demand is admitted, the system will pre-allocate resource to the tenant and pass it to Online Scheduler module, while the rejected demands can be resubmitted by the tenants latter.
The Online Scheduler module performs traffic engineering algorithm (see $\S$ \ref{TE}) every  $T$ (e.g., 10) minutes to enforce bandwidth of each demand.
To prevent much revenue loss, the Online Scheduler module also derives the backup allocation under the assumption that  some fragile links could fail (see $\S$ \ref{backup}) every $T$. 
Each data center has a broker that manages the hosts inside.
Brokers track topology and apportions the allocated rate to each host.
Each host belongs to a service and it maintains a client to enforce bandwidth.

@@

\begin{figure*} 
   \begin{minipage}[t]{0.24\linewidth} 
    \includegraphics[width=1.6 in]{fig/evaluation/routing.pdf}
    \caption{Routings.} 
    \label{routing-version} 
  \end{minipage}% 
   \begin{minipage}[t]{0.24\linewidth} 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}
     \begin{minipage}[t]{0.24\linewidth} 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}
       \begin{minipage}[t]{0.24\linewidth} 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}

\end{figure*}

@@
